---
title: "Exercise 2 - The Six Sigma Method"
author: "Alexander J Ohrt - Statistics for Business Management"
date: "06.10.2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "#>")
setwd("/home/ajo/gitRepos/stat4BusMan/Week4")
```

# Exercise done in place of lecture 

A process is assumed optimal if the production time (in
minutes) per unit is distributed as a Normal (30, 2), i.e. a
normal distribution with mean equal 30 and variance equal 2. A
set of production times are observed for 5, 000 units. The file
“prod.csv” contains the data

```{r}
# Import data. 
Y<-read.csv("prod.csv",sep = ",",col.names = 1)
Y<-as.matrix(Y)
head(Y)
summary(Y)

# Parameters.
mu=30
sigma=sqrt(2)
```


## 1. Calculate the LSL and USL values in a Six Sigma environment.

```{r}
(LSL <- (-6) * sigma + mu)
(USL <- 6 * sigma + mu)
```

As is apparent from the code above, LSL $\approx$ `r round(LSL, 2)` and USL $\approx$ `r round(USL, 2)`.

## 2. Analyse how the actual production process (data set information) is not adapted to Six Sigma environment

First of all, DPMO $\approx$ `r round(1000000*(1-pnorm(USL,mu+1.5*sigma,sigma)), 2)`, as is seen from the output below also. 

```{r}
(DPMO <- 1000000*(1-pnorm(USL,mu+1.5*sigma,sigma)))
```

This means that we will have approximately `r round(DPMO, 1)` defective parts per million opportunities in the long run. Hence, this is a Six Sigma process (This is the theoretical processs). 

Furthermore, the amount of observations that are outside the limits of LSL and USL are 

```{r}
(out <- length(Y[Y>USL | Y < LSL]))
```
which means that 

```{r}
out/dim(Y)[1]*10^6
```
 and hence, from the Sigma Scale table, this is a 4 sigma process. **This is a contradiction, what is correct here?** --> This is the empirical process, while the above shows that the theoretical process is optimal, i.e. Six Sigma.  

Moreover, the code block below shows a plot of LSL, USL, the standard normal probability distribution with mean 0 and mean 1.5 and a histogram of the data. 

```{r}
x <- seq(min(Y), max(Y), length = 100)
f1 <- dnorm(x, mean = mu+1.5*sigma, sd = sigma)
f2 <- dnorm(x, mean = mu, sd = sigma)
hist(Y,xlim = c(LSL,USL),ylim=c(0,0.3),probability = T,main = "", breaks = 50)
lines(x,f1,type="l",lwd=2,lty=2)
lines(x,f2,type="l",lwd=2,lty=1)
abline(v=LSL,lwd=2,lty=2)
abline(v=USL,lwd=2,lty=2)
```

We can see that there are no defects above the USL, which again shows that this is a Six Sigma process. 

## 3. Calculate the number of faults per million following the observed production process.

```{r}
(faults<-sum((Y>USL)+(Y<LSL)))
```

As seen from the calculation above, the number of fault per million is approximately `r faults` (I already found this above also). 


## 4. Obtain the $k\sigma$ process that is adapted to the observed data

```{r}
prob<-faults/nrow(Y)
prob
k<-qnorm(1-prob,1.5,1)
k

sqrt(var(Y))

```

**What does this mean?** --> Hence, one needs to reduce the variance from 2.95 (which is the std in the data, as seen above) to 2 (which is the given std for the theoretical optimal process) in order to reah the optimal process. 

## 5. In Atenea: Calculated $C_p$ also. 
